### 2019-03-25 manuscript.tex
Update manuscript.tex
Cleaning up tex problems

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18).  Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a knick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.)

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of intention of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}

@@

Tables and figures to be included:
- table of basic sociodemographic results
- 3 figures of the results of the 3 models
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/, Fig 1)
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% a chart like figure 8-8D \cite{UNIC13}

@@

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

_ Following up project:
 Threshold on FGC:  based on our finding, mother’s FGC status and community FGC prevalence is a good predictor of daughter’s future FGC status.  We can use newer DHS of multiple nations to predict the future of FGC practice.

@@

\bibliography{refs}

>>>>

\documentclass[12pt,]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{url,hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
\url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a knick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.)

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of intention of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “futureDaughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

Tables and figures to be included:
- table of basic sociodemographic results
- 3 figures of the results of the 3 models
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% a chart like figure 8-8D \cite{UNIC13}

@@

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

_ Following up project:
 Threshold on FGC:  based on our finding, mother’s FGC status and community FGC prevalence is a good predictor of daughter’s future FGC status.  We can use newer DHS of multiple nations to predict the future of FGC practice.  We can use data without fgc benefit module, and that will give us more data than the current 4 nations.

@@

\bibliography{manual}
